SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-04 2017-Xudong-SMT/ActaInformatica.tex
ACTA Paper: Add example of FUN in Example 1 and supplement in page 20.

\QIN{
A possible encoding of such ``Enable'' operator, called $EnableState$, uses a controller $CState$ with three simple control actions $l, r, \delta$ in it to synchronise the behaviour of $P$ and $Q$. Here we use a simple action algebra, containing two constructors $\delta(x)$ and $acc(x)$, for any possible data type of the variable $x$, corresponding to the statements \texttt{exit} and \texttt{accept}. To construct the algebra presentation, we extend the triple $\APres=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$ shown in Table \ref{table:BIPalgebra} with four new constructors. Note that the control action $\delta$ is present by the constructor $\delta$ of arity 0 here which is a different application of the constructor.
}

\QIN{
Another possible encoding of such ``Enable'' operator, called $EnableData$, uses a data-oriented style, with a single state controller $CData$, and a state-variable $v$, with values in $\{0,1\}$. We can use the same algebra presentation as $EnableState$ in this case.
}
\end{example}

@@

\section{Use-Cases}
\label{section:use-cases}
In this section we present the results of open automata construction
for several examples, starting with three constructions from
Section~\ref{section:running-example} using the Enable operator.
Then we give detailed results for the Failure Controller that was
presented in \cite{AVOCS18}, and show how this sort of BIP architectures
can be composed together.
Finally, we give some figures illustrating the benefits of the smart
algorithm on these examples.

@@

The open automata generated for the two encodings of Enable in
Figure~\ref{schema:enable-pnets} are displayed in
Figure~\ref{schema:enable-OAs}.
Note that although these automata look very similar to the PLTS
controllers from Figure~\ref{schema:enable-pnets}, their nature is very
different: they represent the behavior of the whole system, including
the holes $P$ and $Q$. Their transitions do not rely on a particular
implementation of the controllers, but only encode the 
relations between the actions of the holes.
We have shown in \cite{henrio:Forte2016} 
\YX{that the two open automata are equivalent with respect to a notion of FH-bisimulation.}
%how to prove that they are bisimilar.

>>>>

\QIN{
A possible encoding of such ``Enable'' operator, called $EnableState$, uses a controller $CState$ with three simple control actions $l, r, \delta$ in it to synchronise the behaviour of $P$ and $Q$. Here we use a simple action algebra, containing two constructors $\delta(x)$ and $acc(x)$, for any possible data type of the variable $x$, corresponding to the statements \texttt{exit} and \texttt{accept}. To construct the algebra presentation, we extend the triple $\APres=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$ shown in Table \ref{table:BIPalgebra} with four new constructors.}

\QIN{Using the \texttt{FUN} constructor, we express the custom constructors such as $\delta(x)$ in the form of $\texttt{FUN}_{Action, Data}(\delta, x)$ where $x$ is a variable of type $Data$. Here we have $arity(\texttt{FUN}_{Action, Data})=2$ and $\texttt{FUN}_{Action, Data}: Action, Data\to Action$. Note that the control action $\delta$ is present by the constructor $\delta$ of arity 0 here which is a different application of the constructor.
}

\QIN{
Another possible encoding of such ``Enable'' operator, called $EnableData$, uses a data-oriented style, with a single state controller $CData$, and a state-variable $v$, with values in $\{0,1\}$. As there is no more constructor required, we can use the same algebra presentation as $EnableState$ in this case.
}
\end{example}

@@

\section{Use-Cases}
\label{section:use-cases}
In this section we present the results of open automata construction
for several examples, starting with three constructions from
Section~\ref{section:pnets} using the Enable operator.
Then we give detailed results for the Failure Controller that was
presented in \cite{AVOCS18}, and show how this sort of BIP architectures
can be composed together.
Finally, we give some figures illustrating the benefits of the smart
algorithm on these examples.

@@

The open automata generated for the two encodings of Enable in
Figure~\ref{schema:enable-pnets} are displayed in
Figure~\ref{schema:enable-OAs}. 
\QIN{The initial transition of $EnableData$ is transformed to the initialisation of the state variables, here is $\{v\leftarrow1\}$, for its open automata.}
Note that although these automata look very similar to the PLTS
controllers from Figure~\ref{schema:enable-pnets}, their nature is very
different: they represent the behavior of the whole system, including
the holes $P$ and $Q$. Their transitions do not rely on a particular
implementation of the controllers, but only encode the 
relations between the actions of the holes.
We have shown in \cite{henrio:Forte2016} 
\YX{that the two open automata are equivalent with respect to a notion of FH-bisimulation.}
%how to prove that they are bisimilar.
